A data-intensive assessment of the species-abundance distribution.

### 2015-02-17 defense_pres.tex
Adds graphs to presentation.

\documentclass[17pt]{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{tgbonum}
\usepackage{amssymb}
\usepackage{graphicx}
\usefonttheme{structuresmallcapsserif}
\usefonttheme{serif}
\author{Elita Baldridge}
\title{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.1]{../Miscellaneous/Pictures/Weecology.png}} 
%\subject{} 
\begin{document}

@@

\begin{frame}{}

\end{frame}

>>>>

\documentclass{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{tgbonum}
\usepackage{amssymb}
\usepackage{graphicx}
\usefonttheme{structuresmallcapsserif}
\usefonttheme{serif}
\author{Elita Baldridge}
\title[17pt]{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.1]{../Miscellaneous/Pictures/Weecology.png}} 
%\subject{} 
\begin{document}

@@

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter2/taxa_sites.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter2/num_taxa.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.3]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
\end{frame}
